### 2012-03-08 conf joint action --- sharing goals vs sharing intentions cambridge 2012 talk/intention and motor representation in joint action.tex
handout

\section{Slide}
A motor representation is \emph{agent-neutral} if it concerns an action which is not one’s one or, in the case of joint action, not entirely one’s own.

>>>>

\section{Slide}
A motor representation is \emph{agent-neutral} if it concerns an action which is not one’s own or, in the case of joint action, not entirely one’s own.
